A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2023-12-20 paper/paper.tex
Minor

\section{Semantic Typing}
\label{sec:logreldep}
\begin{figure}[h]
  \begin{equation*}
    \begin{split}
      [ [[Bool]] ]_i &= \{ [[a]] \mid [[a =>+ true]] \text{ or } [[a =>+ false]] \} \\
      [ [[Void]] ]_i &= \emptyset \\
      [ [[a ~ b : A]] ]_i &= \{ [[p]] \mid [[p =>+ refl]] \text { and } [[a<=>b]] \}\\
    \end{split}
  \end{equation*}
  \caption{Logical relation for \lang}
  \label{fig:logrel}
\end{figure}

@@

>>>>

\section{Semantic Typing}
\label{sec:logreldep}
\begin{figure}[h]
  \begin{equation*}
    \begin{split}
      [-]_= &:: \mathit{Term} \rightarrow \mathit{Nat} \rightarrow \mathcal{P}(\mathit{Term})\\
      [ [[Void]] ]_i &= \emptyset \\
      [ [[Bool]] ]_i &= \{ [[a]] \mid [[a =>+ true]] \text{ or } [[a =>+ false]] \} \\
      [ [[a ~ b : A]] ]_i &= \{ [[p]] \mid [[p =>+ refl]] \text{ and } [[a<=>b]] \}\\
      [ [[Pi A B]] ]_i &= \{ [[b]] \mid \forall [[a]], \text{ if } [[a]] \in [ [[A]] ]_i\text{, then } [[b a]] \in [ [[B {a}]] ]_i \} \\
      [ [[Set j]] ]_i &= \{ [[A]] \mid [[j < i]] \text{ and } [[A]] \in dom([-]_j) \}\\
      [ [[ A ]] ]_i &= \{ [[a]] \mid \exists [[B]], [[a]] \in[ [[B]] ]_i \text{ and } [[A => B]] \}
    \end{split}
  \end{equation*}
  \caption{Logical relation for \lang}
  \label{fig:logrel}
\end{figure}

@@

The claim that $[ - ]_=$ is a partial function is not immediately
obvious due to the last equation in its definition. The last equation
ensures that the if some type $[[A]]$ is in the domain of the
interpretation function, then any type $[[B]]$ that steps into $[[A]]$
has the same interpretation as $[[A]]$. For example,
since $[[if true Bool Void]]$ steps into $[[Bool]]$, we can say that
$[[if true Bool Void]]$ is semantically inhabited by terms that
reduces down to either $[[true]]$ or $[[false]]$ through the
$[[Bool]]$ case of the interpretation function.

However, due to the non-deterministic nature of parallel reduction,
given some terms $[[A]]$, $[[B0]]$, $[[B1]]$ such that $[[A => B0]]$
and $[[A => B1]]$, the meaning of $[[A]]$ could either be $[ [[B0]] ]_i$
or $[ [[B1]] ]_i$. In fact, the definedness of $[ [[B0]] ]_i$ and $[
[[B1]] ]_i$
should not be taken as granted either. It is unclear for now whether
the definedness of one implies the other.

Fortunately,
